Object Naming in Language and Vision: A Survey and a New Dataset

### 2020-03-12 papers/LREC2020/data-collection.tex
shortens Gemma's new intro

\begin{figure*}[htp]
	\centering
	\includegraphics[height=.8\columnwidth]{figures/distr_imgs-per-domain_VG.png}
	\caption{Overview of the number of images and names per domain in ManyNames.}
	\label{fig:overview_dataset1}
\end{figure*}

>>>>

\begin{figure}[htp]
	\centering
	\includegraphics[width=1\columnwidth]{figures/distr_imgs-per-domain_VG.png}
	\caption{Cumulative histograms of the number of images and names per domain in ManyNames.}
	\label{fig:overview_dataset1}
\end{figure}

### 2020-03-12 papers/LREC2020/intro.tex
shortens Gemma's new intro

% GBT revision:
In this paper, we present a new dataset, ManyNames, to provide richer possibilities for both analysis and modeling of human naming behavior. 
We start by surveying existing resources in L\&V that provide object names,
assessing their potential to contribute to the study of object naming.
While these resources can be exploited for this area of inquiry to some extent (as detailed in Section~\ref{sec:survey})\cs{how remove dot?}, we argue that the low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other. 
This motivates the development of ManyNames, as well as our design choices for it.

% SUBMITTED VERSION:
% Compared to experimental work on perception and language grounding, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
% For instance, picture naming norms used in Psycholinguistics record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
% Consequently, a reliable assessment of inter-annotator agreement, speaker preferences, and a deeper linguistic analysis of the observed variation is mostly not possible with available data collections in  L\&V.
% At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
% A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
ManyNames v.1, the version\cs{would remove "the version"} presented in this paper, contains 36 crowd-sourced names for 25K object instances from \vgenome \cite{krishna2016visualgenome}.%
\footnote{Available at \url{https://github.com/amore-upf/manynames}.}
It is inspired in picture naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
%\gbt{Is it ``picture naming norms'', or ``naming norms''?}
% Naming norms record naming responses for dozens or hundreds of speakers for the same object.
Picture naming norms are typically small (500-1000 images) and use idealized drawings (Figure~\ref{fig:cake}, right; \cs{but see, e.g.,~\cite{brodeur2014bank} for exceptions}); ManyNames is much larger and uses real-world images of objects in complex visual contexts, which makes it suitable for research in L\&V.
%\gbt{should we add footnote citing the naming norms that have real images? (See commented-out tex; \cite{brodeur2014bank} is the ref for the BOSS database.)}
%\cs{see the addition in ref to Figure}

@@

% NEW -- I thought we needed to include this discussion, too.
Object names are rarely used in isolation; typically they are embedded in more complex referring expressions, which are themselves embedded in sentences that are part of discourses or dialogues.
However, in the same way that it has proven useful to model referring expressions in visual scenes in an isolated fashion \cite{Kazemzadeh2014,mao15,Yu2016}, \cs{test models on reasoning abilities over whole scene; we observe instance-based variation, triggered by concrete appearance of object and its context, hence, analogous reasoning is required for naming, too} we believe there is value in modeling object names on their own.
Questions that need addressing regarding object naming are 1)~how much variation in naming is attested and what factors drive the choice of a name (object category? individual properties of the object? context?); see e.g.\ Rohde et al.~\shortcite{rohde2012communicating} and Graf et al.~\shortcite{graf2016animal}, 2)~how to make L\&V models more human-like with respect to naming, improving the design of L\&V architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
\gbt{I looked at the bst file but I don't know how to make the year appear without parentheses inside the parenthesis.}
% ManyNames can inform both theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal} and on the design of L\&V models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
Here, for reasons of scope and space, we provide preliminary results on the amount and type of variation we find in the data.

The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the name \word{cake}, corresponding to the so-called basic-level category, see Section~\ref{sec:rel-work}) and also rich variation (the remaining annotators prefer other options like \word{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \word{dessert} highlights a different facet of the object.

>>>>

% NEW -- I thought we needed to include this discussion, too.
%Object names are rarely used in isolation; typically they are embedded in more complex referring expressions, which are themselves embedded in sentences that are part of discourses or dialogues.
%However, in 
In the same way that it has proven useful to model referring expressions in visual scenes in an isolated fashion, for which systems are required  to integrate and reason over the visual scene and context objects in which an object is presented, %\cite{Kazemzadeh2014,mao15,Yu2016}, 
%\cs{test models on reasoning abilities over whole scene; we observe instance-based variation, triggered by concrete appearance of object and its context, hence, analogous reasoning is required for naming, too} 
we believe there is value in modeling object names on their own. 
Specifically, questions that need addressing regarding object naming are (1)~how much naming variation is attested and what factors drive the choice of a name (object category? individual properties of the object? context?); see e.g.\ Rohde et al.~\shortcite{rohde2012communicating} and Graf et al.~\shortcite{graf2016animal}; (2)~how to make L\&V models more human-like with respect to naming, improving the design of L\&V architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
%\gbt{I looked at the bst file but I don't know how to make the year appear without parentheses inside the parenthesis.}
% ManyNames can inform both theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal} and on the design of L\&V models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).

% GBT revision:
In this paper, we present a new dataset, ManyNames, to provide richer possibilities for both analysis and modeling of human naming behavior. 
%We start by surveying existing resources in L\&V that provide object names, assessing their potential to contribute to the study of object naming.
%While these resources can be exploited for this area of inquiry to some extent (as detailed in Section~\ref{sec:survey})\cs{how remove dot?}, we argue that the low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other. 
Existing resources in L\&V that provide object names can be exploited for this area of inquiry to a limited extent only, as we will detail in Section~\ref{sec:survey}\cs{how remove dot?}, because their low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other. 
We chose a creation methodology for ManyNames to overcome these shortcomings in particular.
%This motivates the development of ManyNames, as well as our design choices for it.

% SUBMITTED VERSION:
% Compared to experimental work on perception and language grounding, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
% For instance, picture naming norms used in Psycholinguistics record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
% Consequently, a reliable assessment of inter-annotator agreement, speaker preferences, and a deeper linguistic analysis of the observed variation is mostly not possible with available data collections in  L\&V.
% At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
% A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
ManyNames~v.1 contains $36$ crowd-sourced names for $25$K object instances from \vgenome \cite{krishna2016visualgenome}.%
\footnote{Available at \url{https://github.com/amore-upf/manynames}.}
It is inspired in picture naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
%\gbt{Is it ``picture naming norms'', or ``naming norms''?}
% Naming norms record naming responses for dozens or hundreds of speakers for the same object.
Picture naming norms are typically small ($500$-$1$K~images) and use idealized drawings (Figure~\ref{fig:cake}, right; but see, e.g.,~\cite{brodeur2014bank} for exceptions); ManyNames is much larger and uses real-world images of objects in complex visual contexts, which makes it suitable for research in L\&V.
%\gbt{should we add footnote citing the naming norms that have real images? (See commented-out tex; \cite{brodeur2014bank} is the ref for the BOSS database.)}
%\cs{see the addition in ref to Figure}

@@

Here, for reasons of scope and space, we provide preliminary results on the amount and type of variation we find in the data.
%
The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the name \word{cake}, corresponding to the so-called basic-level category, see Section~\ref{sec:rel-work}) and also rich variation (the remaining annotators prefer other options like \word{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \word{dessert} highlights a different facet of the object.
